{\bf {\Large Title....}}

### 2016-07-09 ident_manu.Rnw
started identifiability results section

@@

>>>>

<<>>=
data(cat_ident)
data(top_ident)

# percent combos less than gamma 15, 10 by category
collcatpers <- lapply(cat_ident, function(x){

  colls <- x$coll
  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
  c(l15, l10)

  })

# percent combos less than gamma 15, 10 by top in each category
colltoppers <- lapply(top_ident, function(x){

  colls <- x$coll
  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
  c(l15, l10)

  })

The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).  By category, identifiability was lowest for parameter subsets in the phytoplankton (\Sexpr{collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$)  and zooplankton categories (\Sexpr{collcatpers$Zooplankton[1]}\%, \Sexpr{collcatpers$Zooplankton[2]}\%), whereas a majority of combinations for temperature were identifiable (\Sexpr{collcatpers$Temperature[1]}\%, \Sexpr{collcatpers$Temperature[2]}\%).  All subset combinations for optics and organic matter parmeters had $\gamma < 15$.  All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\%, \Sexpr{colltoppers$top4[2]}\%) parameters.  A comparison of average and median identifiability by parameter category or top parameters in each category... something about jump

@@

Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).

### 2016-07-09 ident_manu.tex
started identifiability results section

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Jul 8 16:56:17 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sat Jul 9 14:44:18 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).  By category, identifiability was lowest for parameter subsets in the phytoplankton ($7$\% less than $\gamma = 15$, $5.9$\% less than $\gamma = 10$)  and zooplankton categories ($28.9$\%, $24.2$\%), whereas a majority of combinations for temperature were identifiable ($83.3$\%, $73.3$\%).  All subset combinations for optics and organic matter parmeters had $\gamma < 15$.  All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($77$\% less than $\gamma = 15$, $70.8$\% less than $\gamma = 10$) and top five ($77$\%, $70.8$\%) parameters.  A comparison of average and median identifiability by parameter category or top parameters in each category... something about jump
